Architectures and Open pNets

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: minor change in Ludo's edits

\paragraph{Encoding the interaction model}
First of all, recall that $\nopri[A, \partition ] \bydef{=}
\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
Thus, the holes in the resulting pNet are indexed by the elements of
partition \partition.  For the encoding of our running example, we
take $\partition = \bigl\{\{\PortFail, \PortResume\},\{\PortAsk,
\PortReset\}\bigr\}$.  This corresponds to the intuition that the
dangling ports {\PortFail} and {\PortResume} will be provided by a monitoring component, whereas {\PortAsk} and {\PortReset} correspond to
the actions provided by the ``environment'' (other components of the
system) that are triggered in case of a persistent failure.  Similarly
to the encoding of the coordinators, in the synchronisation vectors of
\nopri[\Gamma], we will associate Boolean values to the actions
corresponding to these ports.

>>>>

\paragraph{Encoding the interaction model}
First of all, recall that $\nopri[A, \partition ] \bydef{=}
\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
Thus, the holes in the resulting pNet are indexed by the elements of
partition \partition.  For the encoding of our running example, we
take $\partition = \bigl\{\{\PortFail, \PortResume\},\{\PortAsk,
\PortReset\}\bigr\}$.  This corresponds to the intuition that the
dangling ports {\PortFail} and {\PortResume} will be provided by a 
monitored component, whereas {\PortAsk} and {\PortReset} correspond to
the actions provided by the ``environment'' (other components of the
system) that are triggered in case of a persistent failure.  Similarly
to the encoding of the coordinators, in the synchronisation vectors of
\nopri[\Gamma], we will associate Boolean values to the actions
corresponding to these ports.
